The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-20 writing/draft3/draft17.tex
writing table of all measure

\textcolor{blue}{re-write the tables with estimates  UNITS KELVIN AND CV TIMES THOUSAND; possibly table of all available weather measure in the appendix, maybe a drop1 and add1 tables??}

@@

>>>>

@@

\begin{table}[H]
\caption{Precipitation and temperature measures considered}\label{vars}
\begin{indented}
\item[]\begin{tabular}{@{}lp{10cm}}
\\[-1em]
\br
\\[-1em]
$\bullet$& Total rainfall over the rainy season\\
$\bullet$& Coefficient of variation of the rainfall during the rainy season\\
$\bullet$& Maximum length of dry spell during the rainy season (in number of days)\\
$\bullet$& Number of drought spells during the rainy season: a drought spell defined as $4$ consecutive days without rain or more\\
$\bullet$& Number of drought spells during the rainy season: a drought spell defined as $10$ consecutive days without rain or more\\
$\bullet$& Number of drought spells during the rainy season: a drought spell defined as $20$ consecutive days without rain or more\\
$\bullet$& Average temperature during the rainy season\\
$\bullet$& Standard deviation of temperature during the rainy season\\
$\bullet$& Cumulative degree days during the rainy season (excluding the days when maximum temperature above $30^{\circ}$C or below $10^{\circ}$C\\
$\bullet$& Number of heatwave days during the rainy season when max. temperature $>35^{\circ}$C
\\
$\bullet$& Maximum daily rainfall  - to control for possible floods
\\
$\bullet$& Sum of precipitation amount on days where precipitation is above $90^{th}$ percentile of precip. of the whole period\\
$\bullet$& Sum of precipitation amount on days where precipitation is above $95^{th}$ percentile of precip. of the whole period\\
$\bullet$& Sum of precipitation amount on days where precipitation is above $99^{th}$ percentile of precip. of the whole period\\
$\bullet$& Number of days where precipitation is above $90^{th}$ percentile of precip. of the whole period\\
$\bullet$& Number of days where precipitation is above $95^{th}$ percentile of precip. of the whole period\\
$\bullet$& Number of days where precipitation is above $99^{th}$ percentile of precip. of the whole period\\
\br
\end{tabular}
\end{indented}

\end{table}
